Transport map accelerated adaptive importance sampling, and application to inverse problems arising from multiscale stochastic reaction networks

### 2018-06-15 TPAIS_2018.tex
Draft complete

We observe this system over the time period $t \in [0,500]$ with
initial condition ******, but we assume that we are only able to observe
the slow variable $S(t)$. 
The effective dynamics of $S$ can be approximated by a system of only
two reactions:
\begin{equation}\label{eqn:QSSA_system}
	\emptyset \xrightarrow{\alpha_1(S)} S \xrightarrow{\bar{\alpha}_4(S)} \emptyset,
\end{equation}
where here the propensities are shown as opposed to the rates.

@@

We create trajectories of this system with the following parameters:****
\begin{equation}
k_1 = ? etc
\end{equation}
over the time period ****$t \in [0,?]$.

>>>>

We observe this system over the time period $t \in [0,500]$ with
initial condition $S_1(0) = S_2(0) = 0$, but we assume that we are only able to observe
the slow variable $S(t) = S_1(t) + S_2(t)$. 
The effective dynamics of $S$ can be approximated by a system of only
two reactions:
\begin{equation}\label{eqn:QSSA_system}
	\emptyset \xrightarrow{\alpha_1(S)} S \xrightarrow{\bar{\alpha}_4(S)} \emptyset,
\end{equation}
where here the propensities are shown as opposed to the rates.

@@

We create trajectories of this system with the following parameters:
\begin{eqnarray*}
k_1 = 0.04, \qquad
k_2 = 5000, \qquad
k_3 = 100, \qquad
k_4 = 1, \\ 
k_5 = 0.5, \qquad
k_6 = 2, \qquad
k_7 = 0.2, \qquad
k_8 = 0.05,
\end{eqnarray*}
over the time period $t \in [0,500]$.
